---
title: "selectionr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{selectionr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(selectionr)
```

# How to use the selectionr package

## Download orthologues from Ensembl
To perform any selection analysis you'll first need a multiple sequences, such as 1-to-1 orthologues from a protein-coding gene. These are easily retrieved using the ensembl.orthologue.download function. This function requires the gene symbol or Ensembl gene ID from a target organism. The sequences for 1-to-1 orthologues will be searched against this database. Then, only species from the desired NCBI target taxon will be downloaded. In this example, we are downloading all primate 1-to-1 sequences, which correspond to the target_taxon 9443 to the current working directory. 

```{r eval=FALSE, include=FALSE}
ensembl.orthologue.download(gene.name = "RBFOX1", target_taxon = 9443, download.directory = ".")
```

